Appendix to "New Metrics for Assessing Projection Pursuit Indexes, and Guiding Optimisation Choices

### 2025-02-18 jso.tex
update supplementary material

\begin{tcolorbox}[enhanced jigsaw, bottomtitle=1mm, titlerule=0mm, opacityback=0, coltitle=black, colback=white, colframe=quarto-callout-note-color-frame, opacitybacktitle=0.6, arc=.35mm, breakable, toptitle=1mm, left=2mm, leftrule=.75mm, title={Algorithm: Jellyfish Optimizer Pseudo Code}, colbacktitle=quarto-callout-note-color!10!white, rightrule=.15mm, bottomrule=.15mm, toprule=.15mm]

@@

In addition, to assess the performance of JSO across various PP
problems, two different data shapes, pipe and a sine wave, are
considered in various dimensional spaces using six different PP indexes:
\texttt{dcor2d\_2}, \texttt{loess2d}, \texttt{MIC}, \texttt{TIC},
\texttt{spline}, and \texttt{stringy}, under varied JSO
hyper-parameters. This results in a total of 76 scenarios, comprising of
30 computed on the pipe data and 46 on the sine-wave data. This study
does not consider dimensions lower than four, as exploring the search
space in such cases is relatively straightforward. Similarly, extremely
high-dimensional cases with complex data structures, where no method can
reliably and consistenly uncover the underlying structure due to the
curse of dimensionality, are also excluded, as they fall outside the
scope of this study. A list of combinations of the data shape,
dimensions and PP indexes that are considered in this study is provided
in Table~\ref{tbl-smoothness-squintability}. Again, JSO is run 50 times
for each scenario to calculate the success rate for each hyper-parameter
combination.

>>>>

\begin{tcolorbox}[enhanced jigsaw, bottomtitle=1mm, colbacktitle=quarto-callout-note-color!10!white, opacityback=0, toprule=.15mm, coltitle=black, rightrule=.15mm, colback=white, toptitle=1mm, colframe=quarto-callout-note-color-frame, bottomrule=.15mm, left=2mm, title={Algorithm: Jellyfish Optimizer Pseudo Code}, arc=.35mm, leftrule=.75mm, breakable, opacitybacktitle=0.6, titlerule=0mm]

@@

In addition, to assess the performance of JSO across various PP
problems, two different data shapes, pipe and a sine wave, are
considered in various dimensional spaces using six different PP indexes:
\texttt{dcor2d\_2}, \texttt{loess2d}, \texttt{MIC}, \texttt{TIC},
\texttt{spline}, and \texttt{stringy}, under varied JSO
hyper-parameters. An example of holes and pipes data with the syntax to
generate them are provided in the supplementary material. This results
in a total of 76 scenarios, comprising of 30 computed on the pipe data
and 46 on the sine-wave data. This study does not consider dimensions
lower than four, as exploring the search space in such cases is
relatively straightforward. Similarly, extremely high-dimensional cases
with complex data structures, where no method can reliably and
consistenly uncover the underlying structure due to the curse of
dimensionality, are also excluded, as they fall outside the scope of
this study. A list of combinations of the data shape, dimensions and PP
indexes that are considered in this study is provided in
Table~\ref{tbl-smoothness-squintability}. Again, JSO is run 50 times for
each scenario to calculate the success rate for each hyper-parameter
combination.

### 2025-02-18 supplementary/index-def.qmd
update supplementary material

```{r setup, echo = FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(tidyverse)
library(ferrn)
library(tourr)
library(tidygraph)
library(ggraph)
library(cassowaryr)
library(patchwork)
```

@@

>>>>

```{r setup, echo = FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(tidyverse)
library(ferrn)
library(tourr)
library(tidygraph)
library(ggraph)
library(cassowaryr)
library(patchwork)
load(here::here("data/sim_pipe_run_best.rda"))
load(here::here("data/sim_sine_6d_spline_head.rda"))
load(here::here("data/sim_sine_6d_spline_best.rda"))
load(here::here("data/sim_sine_6d_spline_projdist.rda"))
load(here::here("data/pipe_better.rda"))
load(here::here("data/pipe_jellyfish.rda"))
load(here::here("data/smoothness.rda"))
load(here::here("data/squintability.rda"))
load(here::here("data/sq_basis_dist_idx.rda"))
load(here::here("data/sim_df.rda"))
```

@@

# The sine and pipe structures in the example data

@fig-plot-data gives an example of the sine and pipe structures data, along with index values for these projections. The syntax to generate these figures are provided below.

```{r, echo = TRUE}
#| label: fig-plot-data
#| fig-width: 10
#| fig-height: 5
#| fig-cap: "The sine and pipe structures in the example data, along with index values for these projections."
data("sine1000")
sine1000 <- as_tibble(sine1000)
dp1 <- ggplot(sine1000, aes(x=V5, y=V6)) + geom_point()
data("pipe1000")
pipe1000 <- as_tibble(pipe1000)
dp2 <- ggplot(pipe1000, aes(x=V5, y=V6)) + geom_point()
dp1 + dp2 + plot_layout(ncol=2)
```
